---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# assignmentb2

<!-- badges: start -->
<!-- badges: end -->

The goal of **assignmentb2** is to demonstrate how to wrap and document a function in an R package. This package uses the pre-baked function `count_all_missing_by_group()` provided by the STAT 545 instructional team. Given a data frame `data` and a column `group`, `count_all_missing_by_group()` creates a new data frame with one row per level of `group`. The first column of the output data frame contains the levels of `group`, and the rest of the columns contain the number of missing values for all columns in `data` except `group`

## Installation

You can install the development version of assignmentb2 from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("zoehorlick/assignmentb2", ref = "1.0.0")
```

## Examples

Here are three examples which show you how to use the function `count_all_missing_by_group()`

```{r}
# Example 1: This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column. 

library(assignmentb2)
count_all_missing_by_group(airquality, Month)
```

```{r}
# Example 2: This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function. 

airquality |>
  count_all_missing_by_group(Month)
```

```{r}
# Example 3: The optional `.groups` argument allows us to keep the output grouped by the grouping column. 

count_all_missing_by_group(airquality, Month, .groups = "keep")
```


