---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# assignmentb2

<!-- badges: start -->
<!-- badges: end -->

The goal of **assignmentb2** is to demonstrate how to wrap and document a function in an R package. This package uses the pre-baked function `count_all_missing_by_group()` provided by the STAT 545 instructional team. The function counts the missing values in a dataset and is grouped by a chosen variable. 

## Installation

You can install the development version of assignmentb2 from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("zoehorlick/assignmentb2")
```

OR, you can use `pak`

```{r}
# install.packages("pak")
pak::pak("zoehorlick/assignmentb2")
```

## Example

This is a basic example which shows you how to use the function `count_all_missing_by_group()`

```{r}
# This example outputs the number of missing values in the airquality dataset grouped by the cyl column
library(assignmentb2)
count_all_missing_by_group(airquality, Month)
```
You can also use pipes: 

```{r}
airquality |>
  count_all_missing_by_group(Month)
```

If you want to keep the output grouped: 

```{r}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.


